MonteCarlo Simulation's of the Covid-19 Pandemic

### 2022-12-15 paper.rmd
Added china figures titles

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(x = "Date", y = "China cumulative number of cases")
positive

ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5)

@@

model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5)

model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```

>>>>

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 1: Total Cases in China from 1/22/2020 to 3/27/2020",
       x = "Date", y = "China cumulative number of cases")
positive

ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 2: Total Deaths in China from 1/22/2020 to 3/27/2020",
       x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 3: Total Cases in China with Gauss Error Function",
       x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5)

@@

model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 4: Total Deaths in China with Gauss Error Function",
       x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 5: Total Cases in China with Day of Flex",
       x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5)

model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  theme(title =element_text(size=6)) +
  labs(title = "Figure 6: Total Deaths in China with Day of Flex",
       x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```
